Supplementary materials for 'Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/supplementary_materials.Rmd
Rename Figure S1

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"))
```

>>>>

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_S1.eps"))
```
